Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions

### 2023-03-24 presentation/index.qmd
calculate MDC and corresponding CIs

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

@@

## Background {transition="convex"}

@@

## But Esben, what about them sleep stages!? {transition="convex"}

@@

## Methods {transition="convex"}

@@

## Features {transition="convex" .H2}

@@

## Human Circadian Clock {transition="convex"}

@@

## Present three modeling approaches

@@

## {.H2 transition="convex"}

@@

### Epoch-Based

@@

### Summarized across nights {.H3}

* Agreement With Zmachine Sleep Stats 
  - Sleep Period Time
  - Total Sleep Time
  - Sleep Efficiency
  - Latency Until Persistent Sleep
  - Wake After Sleep Onset

@@

## Many ROC Curves {transition="convex"}

@@

## Lots of Metrics {transition="convex"}

@@

<!-- ## Bland-Altman Plots {transition="convex"} -->

<!-- ::: {.panel-tabset} -->

<!-- ### Decision Tree -->

<!-- ```{r} -->
<!-- #| echo: false -->
<!-- source(here::here("presentation/code/plot_ba.R")) -->

<!-- dc_plots[[1]] -->

<!-- dc_plots[[2]] -->

<!-- dc_plots[[3]] -->

<!-- dc_plots[[4]] -->

<!-- dc_plots[[5]] -->
<!-- ``` -->

<!-- ### Logistic Regression -->

<!-- ```{r} -->
<!-- lr_plots[[1]] -->

<!-- lr_plots[[2]] -->

<!-- lr_plots[[3]] -->

<!-- lr_plots[[4]] -->

<!-- lr_plots[[5]] -->
<!-- ``` -->

<!-- ### Neural Net -->

<!-- ```{r} -->
<!-- nn_plots[[1]] -->

<!-- nn_plots[[2]] -->

<!-- nn_plots[[3]] -->

<!-- nn_plots[[4]] -->

<!-- nn_plots[[5]] -->
<!-- ``` -->

<!-- ### XGBoost -->

<!-- ```{r} -->
<!-- xg_plots[[1]] -->

<!-- xg_plots[[2]] -->

<!-- xg_plots[[3]] -->

<!-- xg_plots[[4]] -->

<!-- xg_plots[[5]] -->
<!-- ``` -->

<!-- ::: -->

<!-- ## Bland-Altman Analysis {transition="convex" .H2} -->

<!-- ```{r} -->
<!-- source(here::here("presentation/code/table_ba.R")) -->

<!-- tab_ba -->
<!-- ``` -->

<!-- ## In-bed classification flow {transition="convex" .H2} -->

<!-- ```{r} -->
<!-- in_bed_tree <- -->
<!--   read_rds(here::here("data/models/fitted_models/in_bed_simple_CART_fit.rds")) -->

<!-- in_bed_tree |> -->
<!--   extract_fit_engine() |> -->
<!--   visTree( -->
<!--     height = "550px", -->
<!--     nodesPopSize = TRUE, -->
<!--     minNodeSize = 10, -->
<!--     maxNodeSize = 30, -->
<!--     fallenLeaves = TRUE, -->
<!--     legend = FALSE, -->
<!--     digits = 3, -->
<!--     direction = "UD", -->
<!--     colorVar = c( -->
<!--       "#CC5500", "#8B0000", "#FFD700", -->
<!--       "#228B22", "#654321", "#8B0000", "#FFDB58" -->
<!--     ), -->
<!--     export = FALSE -->
<!--   ) |> -->
<!--   visNodes(font = list( -->
<!--     color = "#EEE8D5", -->
<!--     size = 20, -->
<!--     strokeWidth = 1 -->
<!--   )) |> -->
<!--   visEdges(font = list( -->
<!--     color = "#EEE8D5", -->
<!--     size = 20, -->
<!--     strokeWidth = 1 -->
<!--   )) |> -->
<!--   visInteraction( -->
<!--     dragNodes = FALSE, -->
<!--     dragView = FALSE, -->
<!--     zoomView = FALSE -->
<!--   ) -->
<!-- ``` -->

<!-- --- -->

<!-- ## Sleep classification flow {transition="convex" .H2} -->

<!-- ```{r} -->
<!-- sleep_tree <- -->
<!--   read_rds(here::here("data/models/fitted_models/sleep_simple_CART_fit.rds")) -->

<!-- sleep_tree |> -->
<!--   extract_fit_engine() |> -->
<!--   visTree( -->
<!--     height = "550px", -->
<!--     nodesPopSize = TRUE, -->
<!--     minNodeSize = 10, -->
<!--     maxNodeSize = 30, -->
<!--     fallenLeaves = TRUE, -->
<!--     legend = FALSE, -->
<!--     digits = 3, -->
<!--     direction = "UD", -->
<!--     colorVar = c( -->
<!--       "#CC5500", "#8B0000", "#FFD700", -->
<!--       "#228B22", "#654321", "#8B0000", "#FFDB58" -->
<!--     ), -->
<!--     export = FALSE -->
<!--   ) |> -->
<!--   visNodes(font = list( -->
<!--     color = "#EEE8D5", -->
<!--     strokeWidth = 1 -->
<!--   )) |> -->
<!--   visEdges(font = list( -->
<!--     color = "#EEE8D5", -->
<!--     strokeWidth = 1 -->
<!--   )) |> -->
<!--   visInteraction( -->
<!--     dragNodes = FALSE, -->
<!--     dragView = FALSE, -->
<!--     zoomView = FALSE -->
<!--   ) -->
<!-- ``` -->

<!-- ## Discussion {transition="convex"} -->

<!-- - heteroscedasticity -->
<!-- - Cheung 2018 table 4: actigraphy provides a sufficiently narrow range of possible mean differences (CI 95%) clinical significant thresholds -->
<!-- - could be interesting to build models on thigh and hip ocmbined. -->
<!-- - multiclass vs multilabel classification -->
<!-- - in-bed awake/sleep is highly imbalanced -> maybe train a new classifier accounting for imbalanced data (SMOTE) -->
<!-- - model combined preds instead? -->

>>>>

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(visNetwork)
library(tidymodels)
library(tidyverse)
```

@@

## Background {transition="convex" .smaller}

@@

## But Esben, what about them sleep stages!? {transition="convex" .smaller}

@@

## Methods {transition="convex" .smaller}

@@

## Features {transition="convex" .H2 .smaller}

@@

## Human Circadian Clock {transition="convex" .smaller}

@@

## Present three modeling approaches  {.smaller}

@@

## {.H2 transition="convex" .smaller}

@@

### Epoch-Based {.smaller}

@@

### Summarized across nights {.H3 .smaller}

* Agreement With Zmachine Sleep Stats 
  - Sleep Period Time
  - Total Sleep Time
  - Sleep Efficiency
  - Latency Until Persistent Sleep
  - Wake After Sleep Onset
* Minimal Detectable Change

@@

## Many ROC Curves {transition="convex" .H2}

@@

## Lots of Metrics {transition="convex" .H2}

@@

## Bland-Altman Plots {transition="convex" .smaller}

::: {.panel-tabset}

### Sleep Period Time {.smaller}

```{r}
#| echo: false
source(here::here("presentation/code/plot_ba_metric-wise.R"))

spt_plots[[1]]

spt_plots[[2]]

spt_plots[[3]]

spt_plots[[4]]
```

### Total Sleep Time {.smaller}

```{r}
tst_plots[[1]]

tst_plots[[2]]

tst_plots[[3]]

tst_plots[[4]]
```

### Sleep Effeciency {.smaller}

```{r}
se_plots[[1]]

se_plots[[2]]

se_plots[[3]]

se_plots[[4]]
```

### Latency Until Persistant Sleep {.smaller}

```{r}
lps_plots[[1]]

lps_plots[[2]]

lps_plots[[3]]

lps_plots[[4]]
```

### Wake After Sleep Onset {.smaller}

```{r}
waso_plots[[1]]

waso_plots[[2]]

waso_plots[[3]]

waso_plots[[4]]
```

## Bland-Altman Analysis {transition="convex" .H2}

```{r}
source(here::here("presentation/code/table_ba.R"))

tab_ba_crude
```

## In-bed classification flow {transition="convex" .H2}

```{r}
read_rds(here::here("/media/esbenlykke/My Passport/crude/fitted_models/axed_models/decision_tree_in_bed_AXED.rds")) %>%
  extract_fit_engine() |>
  visTree(
    height = "550px",
    nodesPopSize = TRUE,
    minNodeSize = 10,
    maxNodeSize = 30,
    fallenLeaves = TRUE,
    legend = FALSE,
    digits = 3,
    direction = "UD",
    colorVar = c(
      "#CC5500", "#8B0000", "#FFD700",
      "#228B22", "#654321", "#8B0000", "#FFDB58"
    ),
    export = FALSE
  ) |>
  visNodes(font = list(
    color = "#EEE8D5",
    size = 20,
    strokeWidth = 1
  )) |>
  visEdges(font = list(
    color = "#EEE8D5",
    size = 20,
    strokeWidth = 1
  )) |>
  visInteraction(
    dragNodes = FALSE,
    dragView = FALSE,
    zoomView = FALSE
  )
```

## Sleep classification flow {transition="convex" .H2}

```{r}
read_rds(here::here("/media/esbenlykke/My Passport/crude/fitted_models/axed_models/decision_tree_sleep_AXED.rds")) %>% 
  extract_fit_engine() |>
  visTree(
    height = "550px",
    nodesPopSize = TRUE,
    minNodeSize = 10,
    maxNodeSize = 30,
    fallenLeaves = TRUE,
    legend = FALSE,
    digits = 3,
    direction = "UD",
    colorVar = c(
      "#CC5500", "#8B0000", "#FFD700",
      "#228B22", "#654321", "#8B0000", "#FFDB58"
    ),
    export = FALSE
  ) |>
  visNodes(font = list(
    color = "#EEE8D5",
    strokeWidth = 1
  )) |>
  visEdges(font = list(
    color = "#EEE8D5",
    strokeWidth = 1
  )) |>
  visInteraction(
    dragNodes = FALSE,
    dragView = FALSE,
    zoomView = FALSE
  )
```

# Discussion {transition="convex"}

## Discussion {transition="convex" .smaller}

- heteroscedasticity
- Cheung 2018 table 4: actigraphy provides a sufficiently narrow range of possible mean differences (CI 95%) clinical significant thresholds
- could be interesting to build models on thigh and hip ocmbined.
- multiclass vs multilabel classification
- in-bed awake/sleep is highly imbalanced -> maybe train a new classifier accounting for imbalanced data (SMOTE)
- model combined preds instead?
